Quantum Magic Games

### 2023-07-06 paper/main.tex
paper => example main result

>>>>

\begin{tcbexample}{Nonplanar Graph \(\implies\) Magic}{nplanar-magic}
  Recall that the complete bipartite graph \(K_{3, 3}\) is the intersection
  graph of the magic square. Figure~\ref{fig:k33} shows the
  \(K_{3, 3}\), labelled accordingly to the magic square game
  described in Section~\ref{sec:magic-square}.

  \begin{figure}[H]
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \node (e'0) [vertex, label=above right:{\(e'_{0}\)}, label=above left:{\color{green!50!black!80}\(+I\)}] at (0, 0) {};
        \node (e'1) [vertex, label=above right:{\(e'_{1}\)}, label=above left:{\color{green!50!black!80}\(+I\)}] at (4, 0) {};
        \node (e'2) [vertex, label=above right:{\(e'_{2}\)}, label=above left:{\color{green!50!black!80}\(+I\)}] at (8, 0) {};
        \node (e'3) [vertex, label=below right:{\(e'_{3}\)}, label=below left:{\color{red!50!black!80}\(-I\)}] at (0, -3) {};
        \node (e'4) [vertex, label=below right:{\(e'_{4}\)}, label=below left:{\color{red!50!black!80}\(-I\)}] at (4, -3) {};
        \node (e'5) [vertex, label=below right:{\(e'_{5}\)}, label=below left:{\color{red!50!black!80}\(-I\)}] at (8, -3) {};

        \path[]
        (e'0) edge node[midway, fill=gray!15] {\(I \otimes Z\)} (e'3)
        edge node[near start, fill=gray!15, xshift=-.3cm] {\(Z \otimes I\)} (e'4)
        edge node[near start, fill=gray!15] {\(Z \otimes Z\)} (e'5)

        (e'1) edge node[near end, fill=gray!15] {\(X \otimes I\)} (e'3)
        edge node[near end, fill=gray!15] {\(I \otimes X\)} (e'4)
        edge node[near end, fill=gray!15, xshift=0.3cm] {\(X \otimes X\)} (e'5)

        (e'2) edge node[near start, fill=gray!15, xshift=-0.1cm, yshift=.1cm] {\(-X \otimes Z\)} (e'3)
        edge node[near start, fill=gray!15, xshift=0.3cm] {\(-Z \otimes X\)} (e'4)
        edge node[midway, fill=gray!15] {\(Y \otimes Y\)} (e'5)
        ;
      \end{tikzpicture}
    \end{center}
    \caption{\(K_{3, 3}\) corresponding to the magic square arrangement.\label{fig:k33}}
  \end{figure}
  Consider the Petersen graph shown in Figure~\ref{fig:petersen} (a).
  Figure~\ref{fig:petersen} (b) shows the same graph, rewritten in a
  way that it is easy to see that it has the \(K_{3, 3}\) graph as a
  topological minor.

  \begin{figure}[H]
    \begin{subfigure}{0.475\textwidth}
      \begin{center}
        \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
          \foreach \l [
          count=\c,
          evaluate=\c as \ang using {18 + 72*\c},
          evaluate=\c as \e using {iseven(\c - 1)?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
          ] in {0, 1, 2, 3, 4} {
            \node [vertex] (e\l) at (\ang:20mm) {};
            \node at (\ang:24mm) {\(e_{\l}\)};
            \node at ({\ang + 11}:22mm) {\(\e\)};
          }

          \foreach \l [
          count=\c,
          evaluate=\c as \ang using {18 + 72*\c},
          evaluate=\c as \e using {\c>1?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
          ] in {5, 6, 7, 8, 9} {
            \node [vertex] (e\l) at (\ang:10mm) {};
            \node at ({\ang - 18}:12mm) {\(e_{\l}\)};
            \node at ({\ang + 18}:12mm) {\(\e\)};
          }

          \path[]
          (e0) edge (e1) edge (e4) edge (e5)
          (e1) edge (e2) edge (e6)
          (e2) edge (e3) edge (e7)
          (e3) edge (e8) edge (e4)
          (e4) edge (e9)
          (e5) edge (e7) edge (e8)
          (e6) edge (e8) edge (e9)
          (e7) edge (e9)
          ;
        \end{tikzpicture}
      \end{center}
      \caption{}
    \end{subfigure}
    \hfill{}
    \begin{subfigure}{0.475\textwidth}
      \begin{center}
        \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
          \node (e0) [vertex, label=left:{\(e_{0}\)}] at (0, 0) {};
          \node (e2) [vertex, label=left:{\(e_{2}\)}] at (2.5, 0) {};
          \node (e8) [vertex, label=left:{\(e_{8}\)}] at (5, 0) {};
          \node (e1) [vertex, label=left:{\(e_{1}\)}] at (0, -2) {};
          \node (e3) [vertex, label=left:{\(e_{3}\)}] at (2.5, -2) {};
          \node (e5) [vertex, label=below:{\(e_{5}\)}] at (5, -2) {};

          \node (e4) [vertex, label=above:{\(e_{4}\)}] at (1.25, 0) {};
          \node (e6) [vertex, label=below:{\(e_{6}\)}] at (1.25, -2) {};
          \node (e7) [vertex, label=left:{\(e_{7}\)}] at (3.75, -2) {};
          \node (e9) [vertex, label=left:{\(e_{9}\)}] at (3.75, 0) {};

          \path[]
          (e0) edge (e1) edge (e4) edge (e5)
          (e1) edge (e2) edge (e6)
          (e2) edge (e3) edge (e7)
          (e3) edge (e8) edge (e4)
          (e4) edge[bend left] (e9)
          (e5) edge (e7) edge (e8)
          (e6) edge (e8) edge (e9)
          (e7) edge (e9)
          ;
        \end{tikzpicture}
      \end{center}
      \caption{}
    \end{subfigure}
    \caption{Petersen graph.\label{fig:petersen}}
  \end{figure}

  Let \(\phi\) be the function mapping vertices from \(K_{3, 3}\)
  graph to the Petersen graph. Then,
  \begin{align*}
    \phi(e'_{0}) &= e_{0} \\
    \phi(e'_{1}) &= e_{2} \\
    \phi(e'_{2}) &= e_{8} \\
    \phi(e'_{3}) &= e_{1} \\
    \phi(e'_{4}) &= e_{3} \\
    \phi(e'_{5}) &= e_{5}.
  \end{align*}

  Following the proof of Theorem~\ref{theo:main}, we assume that the
  vertices with a correspondence in the \(K_{3, 3}\) graph are
  labelled in the same way, and the remaining are labelled with
  \(+I\).  To construct a quantum realization of the Petersen graph,
  we first look for simples paths that correspond to edges in
  \(K_{3, 3}\). For example, the edge \((e_{0}, e_{1})\) in Petersen
  corresponds exactly to the edge \((e'_{0}, e'_{3})\) in
  \(K_{3, 3}\), so we assign the operator \(I \otimes Z\) to
  it. Similarly, the path \((e_{0}, e_{4}, e_{3})\) in Petersen
  corresponds to the edge \((e'_{0}, e'_{4})\) in \(K_{3, 3}\), so we
  assign the operator \(Z \otimes I\) to both edges \((e_{0}, e_{4})\)
  and \((e_{4}, e_{3})\). We keep doing this for every path that has a
  correspondence in the \(K_{3, 3}\) graph. Then, we label the
  remaining edges with \(+I\). Figure~\ref{fig:petersen-final} shows
  the quantum realization constructed for the Petersen graph.

  \begin{figure}[H]
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \foreach \l [
        count=\c,
        evaluate=\c as \ang using {18 + 72*\c},
        evaluate=\c as \e using {iseven(\c - 1)?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
        ] in {0, 1, 2, 3, 4} {
          \node [vertex] (e\l) at (\ang:30mm) {};
          \node at (\ang:34mm) {\(e_{\l}\)};
          \node at ({\ang + 8}:32mm) {\(\e\)};
        }

        \foreach \l [
        count=\c,
        evaluate=\c as \ang using {18 + 72*\c},
        evaluate=\c as \e using {\c>1?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
        ] in {5, 6, 7, 8, 9} {
          \node [vertex] (e\l) at (\ang:20mm) {};
          \node at ({\ang - 10}:20mm) {\(e_{\l}\)};
          \node at ({\ang + 13}:20mm) {\(\e\)};
        }

        \path[]
        (e0) edge node[midway, fill=gray!15] {\(I \otimes Z\)} (e1)
        edge node[midway, fill=gray!15] {\(Z \otimes I\)} (e4)
        edge node[midway, fill=gray!15] {\(Z \otimes Z\)} (e5)
        (e1) edge node[midway, fill=gray!15] {\(X \otimes I\)} (e2)
        edge node[midway, fill=gray!15, rotate=80] {\(-X \otimes Z\)} (e6)
        (e2) edge node[midway, fill=gray!15] {\(I \otimes X\)} (e3)
        edge node[midway, fill=gray!15, rotate=-30] {\(X \otimes X\)} (e7)
        (e3) edge node[midway, fill=gray!15, rotate=30] {\(-Z \otimes X\)} (e8)
        edge node[midway, fill=gray!15] {\(Z \otimes I\)} (e4)
        (e4) edge node[midway, fill=gray!15, rotate=-30] {\(+I\)} (e9)
        (e5) edge node[midway, fill=gray!15] {\(X \otimes X\)} (e7) edge node[midway, fill=gray!15] {\(Y \otimes Y\)} (e8)
        (e6) edge node[midway, fill=gray!15, rotate=45] {\(-X \otimes Z\)} (e8)
        edge node[midway, fill=gray!15] {\(+I\)} (e9)
        (e7) edge node[midway, fill=gray!15, rotate=-45] {\(+I\)} (e9)
        ;
      \end{tikzpicture}
    \end{center}
    \caption{Quantum realiation of the Petersen graph, constructed from \(K_{3, 3}\) (magic square)}
    \label{fig:petersen-final}
  \end{figure}
\end{tcbexample}
